---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: lumen
---

Remember that low scores mean less violations! Restaurants with a score between 0 and 13 points earn an A, those with 14 to 27 points receive a B and those with 28 or more a C.

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(p8105.datasets)
library(plotly)

data("rest_inspec")

salad_inspec =
  rest_inspec |>
  separate(
    grade_date, into = c("year", "month", "day"), sep = "-") |>
  rename(
    name = dba,
    id = camis) |>
  mutate(
    boro = str_to_title(boro),
    name = str_to_title(name),
    name = replace(name, name == "Cava Grill", "Cava"),
    name = replace(name, name == "Cava Mezze Grill", "Cava")) |>
  filter(
    name %in% c("Sweetgreen", "Just Salad", "Cava", "Fresh & Co")) |>
  drop_na() |>
  select(
    name, year, inspection_date, grade, cuisine_description, critical_flag, action, score, boro, zipcode)
```

Column {data-width=650}
-----------------------------------------------------------------------

### Mean score per restaurant from 2013-2017

This bar plot shows the average score for each restaurant per year from 2013-2017. Since the average score was always below a 13, the average score for each restaurant each year from 2013-2017 was an A. Although Cava performed the best in 2016, this score was an outlier, as only one Cava store was only inspected in 2016.

```{r}
salad_inspec |>
  group_by(name, year) |>
  summarize(
    mean_score = mean(score),
    n_inspections = n()) |>
  mutate(mean_score = round(mean_score, 2)) |>
  mutate(text_label = str_c("Number of inspections that year: ", n_inspections)) |>
  plot_ly(x = ~year, y = ~mean_score, color = ~name, type = "bar", text = ~text_label, colors = "viridis") |>
  layout(
    xaxis = list(title = "Year"),
    yaxis = list(title = "Mean score"))
```

Column {data-width=350}
-----------------------------------------------------------------------

### Distribution of scores per restaurant

This box plot shows the distribution of scores (minimum, 25th percentile, median, 75th percentile, and maximum) for each restaurant from 2013-2017.

```{r}
salad_inspec |>
  plot_ly(x = ~name, y = ~score, color = ~name, type = "box", colors = "viridis") |>
  layout(
    xaxis = list(title = "Restaurant"),
    yaxis = list(title = "Range of scores"))
```

### Scores over time

This scatter plot shows scores over time.

```{r}
salad_inspec |>
  plot_ly(x = ~inspection_date, y = ~score, color = ~name, type = "scatter", mode = "markers", colors = "viridis") |>
  layout(
    xaxis = list(title = "Inspection date"),
    yaxis = list(title = "Score"))
```

